Constraining gravitational wave amplitude birefringence with GWTC-3

### 2022-08-12 src/tex/ms.tex
Update ms.tex

\begin{figure}[h!]
    \script{GW150914_corner.py}
    \includegraphics[width=\columnwidth]{figures/GW150914_corner.png}
    \caption{
        The posterior of $\kappa$, luminosity distance $d_L$ and $\cos{\iota}$ for GW150914.
    The three sets of plots are the PEs done by LIGO with GR \citep{GWTC-2.1, GWTC-3},
    the PE done by us with the frequency independent birefringence and the frequency dependent birefringence respectively.
    Note that there is no posterior of $\kappa$ for the PE from LIGO, as the LIGO PE is based on GR,
    which does not suggest GW amplitude birefringence.
    }
    \label{fig:GW150914_corner}
\end{figure}

>>>>

\begin{figure}[h!]
    \script{GW150914_corner.py}
    \includegraphics[width=\columnwidth]{figures/GW150914_corner.png}
    \caption{
        The posterior of $\kappa$, luminosity distance $d_L$ and $\cos{\iota}$ for GW150914.
    The three sets of plots are the PEs with GR done by LIGO without cosmological reweighing \citep{GWTC-2.1, GWTC-3},
    the PE done by us with the frequency independent birefringence and the frequency dependent birefringence respectively.
    Note that there is no posterior of $\kappa$ for the PE from LIGO, as the LIGO PE is based on GR,
    which does not suggest GW amplitude birefringence.
    }
    \label{fig:GW150914_corner}
\end{figure}
